### 2020-09-06 Manuscript/What.lies.ahead.reviewed.tex
minor changes to TEX file

Among the taxa surveyed, diatoms are of particular interest for their ubiquity in the world's oceans and their important roles in marine food webs \cite{armbrust2009life, wasmund2017diatom}, as well as in ecological and evolutionary theory \cite{margalef11978}. Our model suggests that diatoms will decrease in richness between the present and 2095, particularly in the Hood Canal summer months, when extreme temperatures are more likely. Although the most prevalent response among diatoms is a decrease in suitability, some substantial variability in responses exists within the group. For example, the centric diatom \textit{Coscinodiscus} spp., which is a food source for \textit{Acartia} spp. copepods \cite{jansen2008copepods} and many other animal species, will see future suitable habitat only in colder waters such as those in San Juan Island, while \textit{Skeletonema} spp. and the HAB-forming species \textit{Pseudo-nitzschia} spp. will see their habitat suitability remain constant or slightly increased, especially at low pH levels.

@@

 Changes in environmental conditions and associated shifts in planktonic communities will likely reshape ecosystems and food webs, although some environmental processes may be conserved even as the particular taxa change. A switch from a diatom-dominated ecosystem to one in which dinoflagellate blooms extend in space and time could provoke cascade effects \cite{xiao2018warming} including fish mortality, eutrophication \cite{anderson2002harmful}, and bentho-pelagic coupling \citep[][]{bienfang1984sinking}. Beyond the phylum-specific patterns, the increase in suitable habitat for HAB-forming species will alone be an engine for ecosystem change \cite{trainer2019pelagic, wells2018harmful}.

>>>>

{\color{blue} needs RAMON review}
Among the taxa surveyed, diatoms are of particular interest for their ubiquity in the world's oceans and their important roles in marine food webs \cite{armbrust2009life, wasmund2017diatom}, as well as in ecological and evolutionary theory \cite{margalef11978}. Our model suggests that diatoms will decrease in richness between the present and 2095, particularly in the Hood Canal, where extreme temperatures are more common. Although the most prevalent response among diatoms is a decrease in suitability, some substantial variability in responses exists within the group. For example, the centric diatom \textit{Coscinodiscus} spp., which is a food source for \textit{Acartia} spp. copepods \cite{jansen2008copepods} and many other animal species, will see future suitable habitat only in colder waters such as those in San Juan Island, while \textit{Skeletonema} spp. and the harmful algal bloom (HAB)-forming species \textit{Pseudo-nitzschia} spp. will see their habitat suitability remain constant or slightly increased, especially at low pH levels. {\color{blue} is this in supplement?}

@@

 Changes in environmental conditions and associated shifts in planktonic communities will likely reshape ecosystems and food webs, although some environmental processes may be conserved even as the particular taxa change. A switch from a diatom-dominated ecosystem to one in which dinoflagellate blooms extend in space and time could provoke cascade effects \cite{xiao2018warming} including fish mortality, eutrophication \cite{anderson2002harmful}, and bentho-pelagic coupling \citep[][]{bienfang1984sinking}. Beyond the phylum-specific patterns, the increase in suitable habitat for harmful algae species will alone be an engine for ecosystem change \cite{trainer2019pelagic, wells2018harmful}.
